StackTokens: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-02 fully-abstract-comp/popl2019/paper.tex
Anonymized a sentence.

A more scalable approach retains a single stack that is shared between components.
Enforcing WBCF and LSE in this approach, requires a way to temporarily provide stack and return capabilities to an untrusted component and revoke them after it returns.
While capability revocation is expensive in general, some capability machines offer restricted forms of revocation that can be implemented efficiently.
For example, CHERI offers a form of \emph{local} capabilities that, briefly, can only be stored in registers or on the stack, but not in other parts of memory.
In previous work, we have demonstrated that by making the stack and return pointer local, and a number of security checks and measures, the two properties can be guaranteed~\citep{skorstengaard_reasoning_2017}.
However, a problem with this approach is that revoking the local stack and return capabilities on every boundary crossing requires clearing the entire unused part of the stack, a potentially expensive operation.

>>>>

A more scalable approach retains a single stack that is shared between components.
Enforcing WBCF and LSE in this approach, requires a way to temporarily provide stack and return capabilities to an untrusted component and revoke them after it returns.
While capability revocation is expensive in general, some capability machines offer restricted forms of revocation that can be implemented efficiently.
For example, CHERI offers a form of \emph{local} capabilities that, briefly, can only be stored in registers or on the stack, but not in other parts of memory.
\citet{skorstengaard_reasoning_2017} has demonstrated that by making the stack and return pointer local, and a number of security checks and measures, the two properties can be guaranteed.
However, a problem with this approach is that revoking the local stack and return capabilities on every boundary crossing requires clearing the entire unused part of the stack, a potentially expensive operation.
